---
title: Empirical Studies - Selected"
author: "Jeremiah"
date: "08 May 2018"
output: pdf_document
---

# This RMD file documents the code for the analysis of the Russel 3000 returns data. This is done over a select number of regularisation parameters.

```{r setup, include=FALSE}
# Set working directory
wd = "C:/Users/Michael Tay/Desktop/Project"
# Load libraries and functions
source(paste0(wd,"/functionlist.r"))
library(MASS)
library(LiblineaR)
library(rqPen)
library(quadprog)
library(glmnet)
library(tawny)
library(beepr)
```

## Define Experiment Parameters

```{r}
n.period = 49 # Number of periods tests
p = 500 # Number of assets studied
train.portion = 11/12
test.portion = 1/12
train.size = 231
test.size = 21
```


## Load Returns Data
### Read data generated from previous session
```{r}
returnsdata = read.csv(paste0(wd,"/Russel 3000/returnsdata.csv"))
```

## Initialise arrays to store interested values

```{r}
# Initialise arrays to store the portfolio expected returns
eret.gmv = numeric(n.period)
eret.shr = numeric(n.period)
eret.eq = numeric(n.period)
eret.svr11 = matrix(numeric(11*n.period), 11, n.period)
eret.svr13 = matrix(numeric(11*n.period), 11, n.period)
eret.q25 = matrix(numeric(10*n.period), 10, n.period)
eret.q50 = matrix(numeric(10*n.period), 10, n.period)
eret.q75 = matrix(numeric(10*n.period), 10, n.period)
eret.ls = matrix(numeric(9*n.period), 9, n.period)

# Initialise arrays to store max and min weights
minw.gmv = numeric(n.period)
maxw.gmv = numeric(n.period)
minw.shr = numeric(n.period)
maxw.shr = numeric(n.period)
minw.svr11 = matrix(numeric(11*n.period), 11, n.period)
maxw.svr11 = matrix(numeric(11*n.period), 11, n.period)
minw.svr13 = matrix(numeric(11*n.period), 11, n.period)
maxw.svr13 = matrix(numeric(11*n.period), 11, n.period)
minw.q25 = matrix(numeric(10*n.period), 10, n.period)
maxw.q25 = matrix(numeric(10*n.period), 10, n.period)
minw.q50 = matrix(numeric(10*n.period), 10, n.period)
maxw.q50 = matrix(numeric(10*n.period), 10, n.period)
minw.q75 = matrix(numeric(10*n.period), 10, n.period)
maxw.q75 = matrix(numeric(10*n.period), 10, n.period)
minw.ls = matrix(numeric(9*n.period), 9, n.period)
maxw.ls = matrix(numeric(9*n.period), 9, n.period)

# Initialise arrays to store number of long and short positions
long.gmv = numeric(n.period)
short.gmv = numeric(n.period)
long.shr = numeric(n.period)
short.shr = numeric(n.period)
long.svr11 = matrix(numeric(11*n.period), 11, n.period)
short.svr11 = matrix(numeric(11*n.period), 11, n.period)
long.svr13 = matrix(numeric(11*n.period), 11, n.period)
short.svr13 = matrix(numeric(11*n.period), 11, n.period)
long.q25 = matrix(numeric(10*n.period), 10, n.period)
short.q25 = matrix(numeric(10*n.period), 10, n.period)
long.q50 = matrix(numeric(10*n.period), 10, n.period)
short.q50 = matrix(numeric(10*n.period), 10, n.period)
long.q75 = matrix(numeric(10*n.period), 10, n.period)
short.q75 = matrix(numeric(10*n.period), 10, n.period)
long.ls = matrix(numeric(9*n.period), 9, n.period)
short.ls = matrix(numeric(9*n.period), 9, n.period)

# Initialise matrix to store gross exposure contraint
exp.svr11 = matrix(numeric(11*n.period), 11, n.period)
exp.svr13 = matrix(numeric(11*n.period), 11, n.period)
exp.q25 = matrix(numeric(10*n.period), 10, n.period)
exp.q50 = matrix(numeric(10*n.period), 10, n.period)
exp.q75 = matrix(numeric(10*n.period), 10, n.period)
exp.ls = matrix(numeric(9*n.period), 9, n.period)

# Initialise matrix to store turnover
turnover.gmv = 0
turnover.shr = 0
turnover.eq = 0
turnover.svr11 = numeric(11)
turnover.svr13 = numeric(11)
turnover.q50 = numeric(10)
turnover.q25 = numeric(10)
turnover.q75 = numeric(10)
turnover.ls  = numeric(9)

wtemp.gmv = matrix(numeric(p), p, 1)
wtemp.shr = matrix(numeric(p), p, 1)
wtemp.eq = matrix(numeric(p), p, 1)
wtemp.svr11 = matrix(numeric(11*p), 11, p)
wtemp.svr13 = matrix(numeric(11*p), 11, p)
wtemp.q50 = matrix(numeric(10*p), 10, p)
wtemp.q25 = matrix(numeric(10*p), 10, p)
wtemp.q75 = matrix(numeric(10*p), 10, p)
wtemp.ls = matrix(numeric(9*p), 9, p)
```

## Construct Portfolios (Equally Weighted, SVR11, SVR13)
### First analyse data for p = 500

```{r}
for(i in 1:n.period){
  ### Data Subsetting
  # 11 month study period 1 month test period for 2012 to 2016
  # This is estimated to be 231 data points for training and 21 data points for testing except for year 2012
  if(i == 1){ # not exactly 252 trading days in 2012
    train = returnsdata[1:228, ]*100 # Change to %
    test = returnsdata[229:249, ]*100
  }else{
    test.beg = 229 + (i-1) * 21  # Index of the first data point of current train set
    train = returnsdata[(test.beg - 231):(test.beg - 1), ]*100
    test = returnsdata[test.beg:(test.beg + 20), ]*100
  }

  # Compute Expected Returns of Test Period
  eret = matrix(apply(test, 2, mean), p, 1) # Expected returns of test data
  tret = (apply(as.matrix(test)/100 + 1, 2, prod) - 1)*100
  endret = apply(as.matrix(test)/100 + 1, 2, prod) # For computation of turnover
  
  # Learning Phase ####
  
  ## Compute Estimated Covariance Matrices from train sets
  ### Sample Covariance
  sc = var(train)
  s.shr = cov.shrink(as.matrix(train))
  
  ## GMV Portfolio doesn't exist for degenerate p=500 case
  ### Instead we use the Generalised Inverse
  w.gmv = (ginv(sc)%*%matrix(rep(1,p),p,1))/sum(ginv(sc)%*%matrix(rep(1,p),p,1))
  # Porfolio return
  eret.gmv[i] = tret %*% w.gmv
  minw.gmv[i] = min(w.gmv)
  maxw.gmv[i] = max(w.gmv)
  long.gmv[i] = sum(w.gmv > 0)
  short.gmv[i] = sum(w.gmv < 0)
  # Compute turnover from second period onward
  if(i != 1){
    to = sum(abs(w.gmv - wtemp.gmv))
    turnover.gmv = turnover.gmv + to
  }
  # Find the weights at the end of the period
  w.endret = w.gmv*endret
  endw = w.endret/sum(w.endret)
  wtemp.gmv = endw
  
  ### We can also use the Shrinked Covariance Matrix
  w.shr = (ginv(s.shr)%*%matrix(rep(1,p),p,1))/sum(ginv(s.shr)%*%matrix(rep(1,p),p,1))
  # Porfolio return
  eret.shr[i] = tret %*% w.shr
  minw.shr[i] = min(w.shr)
  maxw.shr[i] = max(w.shr)
  long.shr[i] = sum(w.shr > 0)
  short.shr[i] = sum(w.shr < 0)
  # Compute turnover from second period onward
  if(i != 1){
    to = sum(abs(w.shr - wtemp.shr))
    turnover.shr = turnover.shr + to
  }
  # Find the weights at the end of the period
  w.endret = w.shr*endret
  endw = w.endret/sum(w.endret)
  wtemp.shr = endw
  
  ## Equally Weighted Porfolio
  w.eq = matrix(rep(1/p, p), p, 1)
  # Porfolio return
  eret.eq[i] = tret %*% w.eq
  # Compute turnover from second period onward
  if(i != 1){
    to = sum(abs(w.eq - wtemp.eq))
    turnover.eq = turnover.eq + to
  }
  # Find the weights at the end of the period
  w.endret = w.eq*endret
  endw = w.endret/sum(w.endret)
  wtemp.eq = endw
  
  ## Using SVR ####
  #### Put training returns data into appropriate regression form
  mydat = trans.phi(train)
  y = mydat$Y
  x = as.matrix(mydat[,2:ncol(mydat)])
  
  ### Support Vector Regression LiblineaR - L2-reg, L2-loss (Primal) --> svr11
  ### Test SVR-11 model
  testc = c(1e-05, 5e-05, 1e-04, 5e-04, 1e-03, 5e-03, 1e-02, 5e-02, 0.1, 0.5, 1)
  for(j in 1:length(testc)){
    svr11 = LiblineaR(x, y, type = 11, cost = testc[j], epsilon = 0.01, bias = TRUE, svr_eps = sd(y))
    w.svr11_pm1 = svr11$W[-length(svr11$W)]  # Remove intercept coefficient
    # All weights of magnitude under the threshold 0.001 are considered negligible and excluded
    w.svr11_pm1[abs(w.svr11_pm1) < 0.001] = 0
    # The optimal weights does not include the weight of asset p
    w.svr11_p = 1 - sum(w.svr11_pm1)
    w.svr11 = matrix(c(w.svr11_pm1, w.svr11_p), p, 1)
    
    # Gross Exposure
    exp.svr11[j, i] = sum(abs(w.svr11))
    # Porfolio return
    eret.svr11[j, i] =  tret %*% w.svr11
    # Store min and max weights
    minw.svr11[j, i] = min(w.svr11)
    maxw.svr11[j, i] = max(w.svr11)
    # Store  number of short and long positions
    long.svr11[j, i] = sum(w.svr11 > 0)
    short.svr11[j, i] = sum(w.svr11 < 0)
    # Compute turnover from second period onward
    if(i != 1){
    to = sum(abs(w.svr11 - wtemp.svr11[j, ]))
    turnover.svr11[j] = turnover.svr11[j] + to
    }
    # Find the weights at the end of the period
    w.endret = w.svr11*endret
    endw = w.endret/sum(w.endret)
    wtemp.svr11[j, ] = endw
  }

  ### Support Vector Regression LiblineaR - L2-reg, L1-loss (Dual) --> svr13
  ### Test SVR-13 model
  for(j in 1:length(testc)){
    svr13 = LiblineaR(x, y, type = 13, cost = testc[j], epsilon = 0.01, bias = TRUE, svr_eps = sd(y))
    w.svr13_pm1 = svr13$W[-length(svr13$W)]  # Remove intercept coefficient
    # All weights of magnitude under the threshold 0.001 are considered negligible and excluded
    w.svr13_pm1[abs(w.svr13_pm1) < 0.001] = 0
    # The optimal weights does not include the weight of asset p
    w.svr13_p = 1 - sum(w.svr13_pm1)
    w.svr13 = matrix(c(w.svr13_pm1, w.svr13_p), p, 1)
    
    # Gross Exposure
    exp.svr13[j, i] = sum(abs(w.svr13))
    # Porfolio return
    eret.svr13[j, i] =  tret %*% w.svr13
    # Store min and max weights
    minw.svr13[j, i] = min(w.svr13)
    maxw.svr13[j, i] = max(w.svr13)
    # Store  number of short and long positions
    long.svr13[j, i] = sum(w.svr13 > 0)
    short.svr13[j, i] = sum(w.svr13 < 0)
    # Compute turnover from second period onward
    if(i != 1){
    to = sum(abs(w.svr13 - wtemp.svr13[j, ]))
    turnover.svr13[j] = turnover.svr13[j] + to
    }
    # Find the weights at the end of the period
    w.endret = w.svr13*endret
    endw = w.endret/sum(w.endret)
    wtemp.svr13[j, ] = endw
  }
  if(i %in% seq(5, 50, 5)){
    print(paste("Progress...", paste0(i/5,"/10")))
  }
}
beep(8)
print("Complete!")
```

## Compute Key features of Results from Simulation Studies
### First save the results of the mean returns, SD, Sharpe ratio, Max weight, Min weight and the number of long and short positions from the 500 simulations

```{r}
muret.gmv = mean(eret.gmv)
musd.gmv = sd(eret.gmv)
sharpe.gmv = muret.gmv/musd.gmv
mumaxw.gmv = mean(maxw.gmv)
muminw.gmv = mean(minw.gmv)
mulong.gmv = round(mean(long.gmv))
mushort.gmv = round(mean(short.gmv))
write.csv(muret.gmv, paste0(wd,"/realdata4select/muretgmv.csv"), row.names = F)
write.csv(musd.gmv, paste0(wd,"/realdata4select/musdgmv.csv"), row.names = F)
write.csv(sharpe.gmv, paste0(wd,"/realdata4select/sharpegmv.csv"), row.names = F)
write.csv(mumaxw.gmv, paste0(wd,"/realdata4select/mumaxwgmv.csv"), row.names = F)
write.csv(muminw.gmv, paste0(wd,"/realdata4select/muminwgmv.csv"), row.names = F)
write.csv(mulong.gmv, paste0(wd,"/realdata4select/mulonggmv.csv"), row.names = F)
write.csv(mushort.gmv, paste0(wd,"/realdata4select/mushortgmv.csv"), row.names = F)
write.csv(turnover.gmv, paste0(wd,"/realdata4select/turnovergmv.csv"), row.names = F)

muret.shr = mean(eret.shr)
musd.shr = sd(eret.shr)
sharpe.shr = muret.shr/musd.shr
mumaxw.shr = mean(maxw.shr)
muminw.shr = mean(minw.shr)
mulong.shr = round(mean(long.shr))
mushort.shr = round(mean(short.shr))
write.csv(muret.shr, paste0(wd,"/realdata4select/muretshr.csv"), row.names = F)
write.csv(musd.shr, paste0(wd,"/realdata4select/musdshr.csv"), row.names = F)
write.csv(sharpe.shr, paste0(wd,"/realdata4select/sharpeshr.csv"), row.names = F)
write.csv(mumaxw.shr, paste0(wd,"/realdata4select/mumaxwshr.csv"), row.names = F)
write.csv(muminw.shr, paste0(wd,"/realdata4select/muminwshr.csv"), row.names = F)
write.csv(mulong.shr, paste0(wd,"/realdata4select/mulongshr.csv"), row.names = F)
write.csv(mushort.shr, paste0(wd,"/realdata4select/mushortshr.csv"), row.names = F)
write.csv(turnover.shr, paste0(wd,"/realdata4select/turnovershr.csv"), row.names = F)

muret.eq = mean(eret.eq)
musd.eq = sd(eret.eq)
sharpe.eq = muret.eq/musd.eq
write.csv(muret.eq, paste0(wd,"/realdata4select/mureteq.csv"), row.names = F)
write.csv(musd.eq, paste0(wd,"/realdata4select/musdeq.csv"), row.names = F)
write.csv(sharpe.eq, paste0(wd,"/realdata4select/sharpeeq.csv"), row.names = F)
write.csv(turnover.eq, paste0(wd,"/realdata4select/turnovereq.csv"), row.names = F)

muret.svr11 = apply(eret.svr11, 1, mean)
musd.svr11 = apply(eret.svr11, 1, sd)
sharpe.svr11 = muret.svr11/musd.svr11
mumaxw.svr11 = apply(maxw.svr11, 1, mean)
muminw.svr11 = apply(minw.svr11, 1, mean)
mulong.svr11 = round(apply(long.svr11, 1, mean))
mushort.svr11 = round(apply(short.svr11, 1, mean))
muexp.svr11 = apply(exp.svr11, 1, mean)
write.csv(muexp.svr11, paste0(wd,"/realdata4select/muexpsvr11.csv"), row.names = F)
write.csv(muret.svr11, paste0(wd,"/realdata4select/muretsvr11.csv"), row.names = F)
write.csv(musd.svr11, paste0(wd,"/realdata4select/musdsvr11.csv"), row.names = F)
write.csv(sharpe.svr11, paste0(wd,"/realdata4select/sharpesvr11.csv"), row.names = F)
write.csv(mumaxw.svr11, paste0(wd,"/realdata4select/mumaxwsvr11.csv"), row.names = F)
write.csv(muminw.svr11, paste0(wd,"/realdata4select/muminwsvr11.csv"), row.names = F)
write.csv(mulong.svr11, paste0(wd,"/realdata4select/mulongsvr11.csv"), row.names = F)
write.csv(mushort.svr11, paste0(wd,"/realdata4select/mushortsvr11.csv"), row.names = F)
write.csv(turnover.svr11, paste0(wd,"/realdata4select/turnoversvr11.csv"), row.names = F)

muret.svr13 = apply(eret.svr13, 1, mean)
musd.svr13 = apply(eret.svr13, 1, sd)
sharpe.svr13 = muret.svr13/musd.svr13
mumaxw.svr13 = apply(maxw.svr13, 1, mean)
muminw.svr13 = apply(minw.svr13, 1, mean)
mulong.svr13 = round(apply(long.svr13, 1, mean))
mushort.svr13 = round(apply(short.svr13, 1, mean))
muexp.svr13 = apply(exp.svr13, 1, mean)
write.csv(muexp.svr13, paste0(wd,"/realdata4select/muexpsvr13.csv"), row.names = F)
write.csv(muret.svr13, paste0(wd,"/realdata4select/muretsvr13.csv"), row.names = F)
write.csv(musd.svr13, paste0(wd,"/realdata4select/musdsvr13.csv"), row.names = F)
write.csv(sharpe.svr13, paste0(wd,"/realdata4select/sharpesvr13.csv"), row.names = F)
write.csv(mumaxw.svr13, paste0(wd,"/realdata4select/mumaxwsvr13.csv"), row.names = F)
write.csv(muminw.svr13, paste0(wd,"/realdata4select/muminwsvr13.csv"), row.names = F)
write.csv(mulong.svr13, paste0(wd,"/realdata4select/mulongsvr13.csv"), row.names = F)
write.csv(mushort.svr13, paste0(wd,"/realdata4select/mushortsvr13.csv"), row.names = F)
write.csv(turnover.svr13, paste0(wd,"/realdata4select/turnoversvr13.csv"), row.names = F)
```
## Load data from previous session
```{r}
muret.eq = read.csv(paste0(wd,"/realdata4select/mureteq.csv"))[[1]]
musd.eq = read.csv(paste0(wd,"/realdata4select/musdeq.csv"))[[1]]
sharpe.eq = read.csv(paste0(wd,"/realdata4select/sharpeeq.csv"))[[1]]

muret.svr11 = read.csv(paste0(wd,"/realdata4select/muretsvr11.csv"))[[1]]
musd.svr11 = read.csv(paste0(wd,"/realdata4select/musdsvr11.csv"))[[1]]
sharpe.svr11 = read.csv(paste0(wd,"/realdata4select/sharpesvr11.csv"))[[1]]
mumaxw.svr11 = read.csv(paste0(wd,"/realdata4select/mumaxwsvr11.csv"))[[1]]
muminw.svr11 = read.csv(paste0(wd,"/realdata4select/muminwsvr11.csv"))[[1]]
mulong.svr11 = read.csv(paste0(wd,"/realdata4select/mulongsvr11.csv"))[[1]]
mushort.svr11 = read.csv(paste0(wd,"/realdata4select/mushortsvr11.csv"))[[1]]

muret.svr13 = read.csv(paste0(wd,"/realdata4select/muretsvr13.csv"))[[1]]
musd.svr13 = read.csv(paste0(wd,"/realdata4select/musdsvr13.csv"))[[1]]
sharpe.svr13 = read.csv(paste0(wd,"/realdata4select/sharpesvr13.csv"))[[1]]
mumaxw.svr13 = read.csv(paste0(wd,"/realdata4select/mumaxwsvr13.csv"))[[1]]
muminw.svr13 = read.csv(paste0(wd,"/realdata4select/muminwsvr13.csv"))[[1]]
mulong.svr13 = read.csv(paste0(wd,"/realdata4select/mulongsvr13.csv"))[[1]]
mushort.svr13 = read.csv(paste0(wd,"/realdata4select/mushortsvr13.csv"))[[1]]
```


## Analysis of Results from Simulation Studies with SVR 11
### We look at the mean returns, SD, Sharpe ratio, Max weight, Min weight and the number of long and short positions from the 500 simulations
```{r}
testc = c(1e-05, 5e-05, 1e-04, 5e-04, 1e-03, 5e-03, 1e-02, 5e-02, 0.1, 0.5, 1)
ind = 1:11
testc[ind]
muret.svr11x = muret.svr11[ind]
musd.svr11x = musd.svr11[ind]
sharpe.svr11x = sharpe.svr11[ind]
mumaxw.svr11x = mumaxw.svr11[ind]
muminw.svr11x = muminw.svr11[ind]
mulong.svr11x = mulong.svr11[ind]
mushort.svr11x = mushort.svr11[ind]
turnover.svr11x = turnover.svr11[ind]
print(muret.svr11x)
print(musd.svr11x)
print(sharpe.svr11x)
print(mumaxw.svr11x)
print(muminw.svr11x)
print(mulong.svr11x)
print(mushort.svr11x)
print(turnover.svr11x)
```

## Analysis of Results from Simulation Studies with SVR 13
### We look at the mean returns, SD, Sharpe ratio, Max weight, Min weight and the number of long and short positions from the 500 simulations
```{r}
testc = c(1e-05, 5e-05, 1e-04, 5e-04, 1e-03, 5e-03, 1e-02, 5e-02, 0.1, 0.5, 1)
ind = 1:11
testc[ind]
muret.svr13x = muret.svr13[ind]
musd.svr13x = musd.svr13[ind]
sharpe.svr13x = sharpe.svr13[ind]
mumaxw.svr13x = mumaxw.svr13[ind]
muminw.svr13x = muminw.svr13[ind]
mulong.svr13x = mulong.svr13[ind]
mushort.svr13x = mushort.svr13[ind]
turnover.svr13x = turnover.svr13[ind]
print(muret.svr13x)
print(musd.svr13x)
print(sharpe.svr13x)
print(mumaxw.svr13x)
print(muminw.svr13x)
print(mulong.svr13x)
print(mushort.svr13x)
print(turnover.svr13x)
```

## Analysis of Results from Simulation Studies with Equally Weighted Portfolio
### We look at the mean returns, SD, Sharpe ratio, Max weight, Min weight and the number of long and short positions from the 500 simulations
```{r}
print(muret.eq)
print(musd.eq)
print(sharpe.eq)
print(turnover.eq)
```
## GMV
```{r}
print(muret.gmv)
print(musd.gmv)
print(sharpe.gmv)
print(mumaxw.gmv)
print(muminw.gmv)
print(mulong.gmv)
print(mushort.gmv)
print(turnover.gmv)
```

## Shrinked
```{r}
print(muret.shr)
print(musd.shr)
print(sharpe.shr)
print(mumaxw.shr)
print(muminw.shr)
print(mulong.shr)
print(mushort.shr)
print(turnover.shr)
```

## Construct Portfolios (L1 Regularized Quantile Regression) for p = 500

```{r}
for(i in 1:n.period){
  ### Data Subsetting
  # 11 month study period 1 month test period for 2012 to 2016
  # This is estimated to be 231 data points for training and 21 data points for testing except for year 2012
  if(i == 1){ # not exactly 252 trading days in 2012
    train = returnsdata[1:228, ]*100 # Change to %
    test = returnsdata[229:249, ]*100 # Change to %
  }else{
    test.beg = 229 + (i-1) * 21  # Index of the first data point of current train set
    train = returnsdata[(test.beg - 231):(test.beg - 1), ]*100 # Change to %
    test = returnsdata[test.beg:(test.beg + 20), ]*100 # Change to %
  }

  # Compute Expected Returns of Test Period
  eret = matrix(apply(test, 2, mean), p, 1) # Expected returns of test data
  tret = (apply(as.matrix(test)/100 + 1, 2, prod) - 1)*100
  endret = apply(as.matrix(test)/100 + 1, 2, prod) # For computation of turnover
  
  # Learning Phase ####
  
  ## Compute Estimated Covariance Matrices from train sets
  ### Sample Covariance
  sc = var(train)

  ## Using Quantile Regression ####
  #### Put training returns data into appropriate regression form
  mydat = trans.phi(train)
  y = mydat$Y
  x = as.matrix(mydat[,2:ncol(mydat)])
  
  ### Lasso Penalized Quantile Regression using rqPen
  ### Test Quantile model - 50% Quantile
  ### Dithering the response variable is frequently a useful option in quantile regression fitting to avoid deleterious effects of degenerate solutions     (Machado and Santos Silva, 2005)
  testlam = c(0.001, 0.003, 0.005, 0.008, 0.01, 0.03, 0.05, 0.08, 0.1, 0.5)
  for(j in 1:length(testlam)){
    y50 = y # Dither y50 instead of the actual vector y
    q50 = NULL
    while(is.null(q50)){
      try({q50 = LASSO.fit(y50, x, tau = .5, lambda = testlam[j], intercept = TRUE, coef.cutoff = 1e-03)}, silent = T)
      if(is.null(q50)) y50 = dither(y, type = "symmetric", value = 0.0001)
    }
    # The optimal weights does not include the weight of asset p
    w.q50_p = 1 - sum(q50[2:length(q50)])
    w.q50 = matrix(c(q50[2:length(q50)], w.q50_p), p, 1)
    # Store gross exposure
    exp.q50[j, i] = sum(abs(w.q50))
    # Porfolio return
    eret.q50[j, i] =  tret %*% w.q50
    # Store min and max weights
    minw.q50[j, i] = min(w.q50)
    maxw.q50[j, i] = max(w.q50)
    # Store  number of short and long positions
    long.q50[j, i] = sum(w.q50 > 0)
    short.q50[j, i] = sum(w.q50 < 0)
    # Compute turnover from second period onward
    if(i != 1){
      to = sum(abs(w.q50 - wtemp.q50[j, ]))
      turnover.q50[j] = turnover.q50[j] + to
    }
    # Find the weights at the end of the period
    w.endret = w.q50*endret
    endw = w.endret/sum(w.endret)
    wtemp.q50[j, ] = endw
  }
  
  ### Test Quantile model - 25% Quantile
  for(j in 1:length(testlam)){
    y25 = y # Dither y25 instead of the actual vector y
    q25 = NULL
    while(is.null(q25)){
      try({q25 = LASSO.fit(y25, x, tau = .25, lambda = testlam[j], intercept = TRUE, coef.cutoff = 1e-03)}, silent = T)
      if(is.null(q25)) y25 = dither(y25, type = "symmetric", value = 0.0001)
    }
    # The optimal weights does not include the weight of asset p
    w.q25_p = 1 - sum(q25[2:length(q25)])
    w.q25 = matrix(c(q25[2:length(q25)], w.q25_p), p, 1)
    # Store gross exposure
    exp.q25[j, i] = sum(abs(w.q25))
    # Porfolio return
    eret.q25[j, i] =   tret %*% w.q25
    # Store min and max weights
    minw.q25[j, i] = min(w.q25)
    maxw.q25[j, i] = max(w.q25)
    # Store  number of short and long positions
    long.q25[j, i] = sum(w.q25 > 0)
    short.q25[j, i] = sum(w.q25 < 0)
    # Compute turnover from second period onward
    if(i != 1){
      to = sum(abs(w.q25 - wtemp.q25[j, ]))
      turnover.q25[j] = turnover.q25[j] + to
    }
    # Find the weights at the end of the period
    w.endret = w.q25*endret
    endw = w.endret/sum(w.endret)
    wtemp.q25[j, ] = endw
  }
    
  ### Test Quantile model - 75% Quantile
  for(j in 1:length(testlam)){
    y75 = y # Dither y75 instead of the actual vector y
    q75 = NULL
    while(is.null(q75)){
      try({q75 = LASSO.fit(y75, x, tau = .75, lambda = testlam[j], intercept = TRUE, coef.cutoff = 1e-03)}, silent = T)
      if(is.null(q75)) y75 = dither(y75, type = "symmetric", value = 0.0001)
    }
    # The optimal weights does not include the weight of asset p
    w.q75_p = 1 - sum(q75[2:length(q75)])
    w.q75 = matrix(c(q75[2:length(q75)], w.q75_p), p, 1)
    # Store gross exposure
    exp.q75[j, i] = sum(abs(w.q75))
    # Porfolio return
    eret.q75[j, i] =   tret %*% w.q75
    # Store min and max weights
    minw.q75[j, i] = min(w.q75)
    maxw.q75[j, i] = max(w.q75)
    # Store  number of short and long positions
    long.q75[j, i] = sum(w.q75 > 0)
    short.q75[j, i] = sum(w.q75 < 0)
    # Compute turnover from second period onward
    if(i != 1){
      to = sum(abs(w.q75 - wtemp.q75[j, ]))
      turnover.q75[j] = turnover.q75[j] + to
    }
    # Find the weights at the end of the period
    w.endret = w.q75*endret
    endw = w.endret/sum(w.endret)
    wtemp.q75[j, ] = endw
  }
  if(i %in% seq(5, 50, 5)){
    print(paste("Progress...", paste0(i/5,"/10")))
  }
}
beep(8)
print("Complete!")

```

## Save Results
```{r}
muret.q50 = apply(eret.q50, 1, mean)
musd.q50 = apply(eret.q50, 1, sd)
sharpe.q50 = muret.q50/musd.q50
mumaxw.q50 = apply(maxw.q50, 1, mean)
muminw.q50 = apply(minw.q50, 1, mean)
mulong.q50 = round(apply(long.q50, 1, mean))
mushort.q50 = round(apply(short.q50, 1, mean))
muexp.q50 = apply(exp.q50, 1, mean)
write.csv(muexp.q50, paste0(wd,"/realdata4select/muexpq502.csv"), row.names = F)
write.csv(muret.q50, paste0(wd,"/realdata4select/muretq502.csv"), row.names = F)
write.csv(musd.q50, paste0(wd,"/realdata4select/musdq502.csv"), row.names = F)
write.csv(sharpe.q50, paste0(wd,"/realdata4select/sharpeq502.csv"), row.names = F)
write.csv(mumaxw.q50, paste0(wd,"/realdata4select/mumaxwq502.csv"), row.names = F)
write.csv(muminw.q50, paste0(wd,"/realdata4select/muminwq502.csv"), row.names = F)
write.csv(mulong.q50, paste0(wd,"/realdata4select/mulongq502.csv"), row.names = F)
write.csv(mushort.q50, paste0(wd,"/realdata4select/mushortq502.csv"), row.names = F)
write.csv(turnover.q50, paste0(wd,"/realdata4select/turnoverq502.csv"), row.names = F)


muret.q25 = apply(eret.q25, 1, mean)
musd.q25 = apply(eret.q25, 1, sd)
sharpe.q25 = muret.q25/musd.q25
mumaxw.q25 = apply(maxw.q25, 1, mean)
muminw.q25 = apply(minw.q25, 1, mean)
mulong.q25 = round(apply(long.q25, 1, mean))
mushort.q25 = round(apply(short.q25, 1, mean))
muexp.q25 = apply(exp.q25, 1, mean)
write.csv(muexp.q25, paste0(wd,"/realdata4select/muexpq252.csv"), row.names = F)
write.csv(muret.q25, paste0(wd,"/realdata4select/muretq252.csv"), row.names = F)
write.csv(musd.q25, paste0(wd,"/realdata4select/musdq252.csv"), row.names = F)
write.csv(sharpe.q25, paste0(wd,"/realdata4select/sharpeq252.csv"), row.names = F)
write.csv(mumaxw.q25, paste0(wd,"/realdata4select/mumaxwq252.csv"), row.names = F)
write.csv(muminw.q25, paste0(wd,"/realdata4select/muminwq252.csv"), row.names = F)
write.csv(mulong.q25, paste0(wd,"/realdata4select/mulongq252.csv"), row.names = F)
write.csv(mushort.q25, paste0(wd,"/realdata4select/mushortq252.csv"), row.names = F)
write.csv(turnover.q25, paste0(wd,"/realdata4select/turnoverq252.csv"), row.names = F)


muret.q75 = apply(eret.q75, 1, mean)
musd.q75 = apply(eret.q75, 1, sd)
sharpe.q75 = muret.q75/musd.q75
mumaxw.q75 = apply(maxw.q75, 1, mean)
muminw.q75 = apply(minw.q75, 1, mean)
mulong.q75 = round(apply(long.q75, 1, mean))
mushort.q75 = round(apply(short.q75, 1, mean))
muexp.q75 = apply(exp.q75, 1, mean)
write.csv(muexp.q75, paste0(wd,"/realdata4select/muexpq752.csv"), row.names = F)
write.csv(muret.q75, paste0(wd,"/realdata4select/muretq752.csv"), row.names = F)
write.csv(musd.q75, paste0(wd,"/realdata4select/musdq752.csv"), row.names = F)
write.csv(sharpe.q75, paste0(wd,"/realdata4select/sharpeq752.csv"), row.names = F)
write.csv(mumaxw.q75, paste0(wd,"/realdata4select/mumaxwq752.csv"), row.names = F)
write.csv(muminw.q75, paste0(wd,"/realdata4select/muminwq752.csv"), row.names = F)
write.csv(mulong.q75, paste0(wd,"/realdata4select/mulongq752.csv"), row.names = F)
write.csv(mushort.q75, paste0(wd,"/realdata4select/mushortq752.csv"), row.names = F)
write.csv(turnover.q75, paste0(wd,"/realdata4select/turnoverq752.csv"), row.names = F)
```

## Load data
```{r}
# q50
muret.q50 = read.csv(paste0(wd,"/realdata4select/muretq50.csv"))[[1]]
musd.q50 = read.csv(paste0(wd,"/realdata4select/musdq50.csv"))[[1]]
sharpe.q50 = read.csv(paste0(wd,"/realdata4select/sharpeq50.csv"))[[1]]
mumaxw.q50 = read.csv(paste0(wd,"/realdata4select/mumaxwq50.csv"))[[1]]
muminw.q50 = read.csv(paste0(wd,"/realdata4select/muminwq50.csv"))[[1]]
mulong.q50 = read.csv(paste0(wd,"/realdata4select/mulongq50.csv"))[[1]]
mushort.q50 = read.csv(paste0(wd,"/realdata4select/mushortq50.csv"))[[1]]
muexp.q50 = read.csv(paste0(wd,"/realdata4select/muexpq50.csv"))[[1]]
turnover.q50 = read.csv(paste0(wd,"/realdata4select/turnoverq50.csv"))[[1]]

# q25
muret.q25 = read.csv(paste0(wd,"/realdata4select/muretq25.csv"))[[1]]
musd.q25 = read.csv(paste0(wd,"/realdata4select/musdq25.csv"))[[1]]
sharpe.q25 = read.csv(paste0(wd,"/realdata4select/sharpeq25.csv"))[[1]]
mumaxw.q25 = read.csv(paste0(wd,"/realdata4select/mumaxwq25.csv"))[[1]]
muminw.q25 = read.csv(paste0(wd,"/realdata4select/muminwq25.csv"))[[1]]
mulong.q25 = read.csv(paste0(wd,"/realdata4select/mulongq25.csv"))[[1]]
mushort.q25 = read.csv(paste0(wd,"/realdata4select/mushortq25.csv"))[[1]]
muexp.q25 = read.csv(paste0(wd,"/realdata4select/muexpq25.csv"))[[1]]
turnover.q25 = read.csv(paste0(wd,"/realdata4select/turnoverq25.csv"))[[1]]

# q75
muret.q75 = read.csv(paste0(wd,"/realdata4select/muretq75.csv"))[[1]]
musd.q75 = read.csv(paste0(wd,"/realdata4select/musdq75.csv"))[[1]]
sharpe.q75 = read.csv(paste0(wd,"/realdata4select/sharpeq75.csv"))[[1]]
mumaxw.q75 = read.csv(paste0(wd,"/realdata4select/mumaxwq75.csv"))[[1]]
muminw.q75 = read.csv(paste0(wd,"/realdata4select/muminwq75.csv"))[[1]]
mulong.q75 = read.csv(paste0(wd,"/realdata4select/mulongq75.csv"))[[1]]
mushort.q75 = read.csv(paste0(wd,"/realdata4select/mushortq75.csv"))[[1]]
muexp.q75 = read.csv(paste0(wd,"/realdata4select/muexpq75.csv"))[[1]]
turnover.q75 = read.csv(paste0(wd,"/realdata4select/turnoverq75.csv"))[[1]]
```

## Analysis of Results from Empirical Studies with quantile regression, Q50
### We look at the mean returns, SD, Sharpe ratio, Max weight, Min weight and the number of long and short positions from the 500 simulations
```{r}
# q50
testlam = c(0.001, 0.003, 0.005, 0.008, 0.01, 0.03, 0.05, 0.08, 0.1, 0.5)
ind2 = 4:10
testlam[ind2]
muret.q50x = muret.q50[ind2]
musd.q50x = musd.q50[ind2]
sharpe.q50x = sharpe.q50[ind2]
mumaxw.q50x = mumaxw.q50[ind2]
muminw.q50x = muminw.q50[ind2]
mulong.q50x = mulong.q50[ind2]
mushort.q50x = mushort.q50[ind2]
turnover.q50x = turnover.q50[ind2]
print(muret.q50x)
print(musd.q50x)
print(sharpe.q50x)
print(mumaxw.q50x)
print(muminw.q50x)
print(mulong.q50x)
print(mushort.q50x)
print(turnover.q50x)
```
## Analysis of Results from Empirical Studies with quantile regression, Q25
### We look at the mean returns, SD, Sharpe ratio, Max weight, Min weight and the number of long and short positions from the 500 simulations
```{r}
# q25
testlam = c(0.001, 0.003, 0.005, 0.008, 0.01, 0.03, 0.05, 0.08, 0.1, 0.5)
ind2 = 4:10
testlam[ind2]
muret.q25x = muret.q25[ind2]
musd.q25x = musd.q25[ind2]
sharpe.q25x = sharpe.q25[ind2]
mumaxw.q25x = mumaxw.q25[ind2]
muminw.q25x = muminw.q25[ind2]
mulong.q25x = mulong.q25[ind2]
mushort.q25x = mushort.q25[ind2]
turnover.q25x = turnover.q25[ind2]
print(muret.q25x)
print(musd.q25x)
print(sharpe.q25x)
print(mumaxw.q25x)
print(muminw.q25x)
print(mulong.q25x)
print(mushort.q25x)
print(turnover.q25x)
```
## Analysis of Results from Empirical Studies with quantile regression, Q75
### We look at the mean returns, SD, Sharpe ratio, Max weight, Min weight and the number of long and short positions from the 500 simulations
```{r}
# q75
testlam = c(0.001, 0.003, 0.005, 0.008, 0.01, 0.03, 0.05, 0.08, 0.1, 0.5)
ind2 = 4:10
testlam[ind2]
muret.q75x = muret.q75[ind2]
musd.q75x = musd.q75[ind2]
sharpe.q75x = sharpe.q75[ind2]
mumaxw.q75x = mumaxw.q75[ind2]
muminw.q75x = muminw.q75[ind2]
mulong.q75x = mulong.q75[ind2]
mushort.q75x = mushort.q75[ind2]
turnover.q75x = turnover.q75[ind2]
print(muret.q75x)
print(musd.q75x)
print(sharpe.q75x)
print(mumaxw.q75x)
print(muminw.q75x)
print(mulong.q75x)
print(mushort.q75x)
print(turnover.q75x)
```

## Construct Portfolios (L1 Regularized Regression - LASSO) for RUSSEL
```{r}
for(i in 1:n.period){
  ### Data Subsetting
  # 11 month study period 1 month test period for 2012 to 2016
  # This is estimated to be 231 data points for training and 21 data points for testing except for year 2012
  if(i == 1){ # not exactly 252 trading days in 2012
    train = returnsdata[1:228, ]*100 # Change to %
    test = returnsdata[229:249, ]*100 # Change to %
  }else{
    test.beg = 229 + (i-1) * 21  # Index of the first data point of current train set
    train = returnsdata[(test.beg - 231):(test.beg - 1), ]*100 # Change to %
    test = returnsdata[test.beg:(test.beg + 20), ]*100 # Change to %
  }

  # Compute Expected Returns of Test Period
  eret = matrix(apply(test, 2, mean), p, 1) # Expected returns of test data
  tret = (apply(as.matrix(test)/100 + 1, 2, prod) - 1)*100
  endret = apply(as.matrix(test)/100 + 1, 2, prod) # For computation of turnover
    
  # Learning Phase ####
  
  ## Compute Estimated Covariance Matrices from train sets
  ### Sample Covariance
  sc = var(train)

  #### Put training returns data into appropriate regression form
  mydat = trans.phi(train)
  y = mydat$Y
  x = as.matrix(mydat[,2:ncol(mydat)])
  
  ### Lasso Regression
  testlam = c(1e-04, 5e-04, 1e-03, 5e-03, 1e-02, 5e-02, 1e-01, 5e-01, 1)
  ls.net = glmnet(x, y, alpha = 1, lambda = testlam)
  ls = coef(ls.net)
  for(j in 1:length(testlam)){
    w.ls_pm1.temp = ls[ ,j]
    w.ls_pm1 = w.ls_pm1.temp[2:length(w.ls_pm1.temp)] # First asset is the intercept
    w.ls_p = 1 - sum(w.ls_pm1)
    w.ls = matrix(c(w.ls_pm1, w.ls_p), p, 1)
    # Store gross exposure
    exp.ls[j, i] = sum(abs(w.ls))
    # Porfolio return
    eret.ls[j, i] =   tret %*% w.ls
    # Store min and max weights
    minw.ls[j, i] = min(w.ls)
    maxw.ls[j, i] = max(w.ls)
    # Store  number of short and long positions
    long.ls[j, i] = sum(w.ls > 0)
    short.ls[j, i] = sum(w.ls < 0)
    # Compute turnover from second period onward
    if(i != 1){
      to = sum(abs(t(w.ls) - wtemp.ls[j, ]))
      turnover.ls[j] = turnover.ls[j] + to
    }
    # Find the weights at the end of the period
    w.endret = w.ls*endret
    endw = w.endret/sum(w.endret)
    wtemp.ls[j, ] = endw
  }
  if(i %in% seq(5, 50, 5)){
      print(paste("Progress...", paste0(i/5,"/10")))
  }
}
beep(8)
print("Complete!")
```

## Save Results
```{r}
muret.ls = apply(eret.ls, 1, mean)
musd.ls = apply(eret.ls, 1, sd)
sharpe.ls = muret.ls/musd.ls
mumaxw.ls = apply(maxw.ls, 1, mean)
muminw.ls = apply(minw.ls, 1, mean)
mulong.ls = round(apply(long.ls, 1, mean))
mushort.ls = round(apply(short.ls, 1, mean))
muexp.ls = apply(exp.ls, 1, mean)
write.csv(muexp.ls, paste0(wd,"/realdata4select/muexpls.csv"), row.names = F)
write.csv(muret.ls, paste0(wd,"/realdata4select/muretls.csv"), row.names = F)
write.csv(musd.ls, paste0(wd,"/realdata4select/musdls.csv"), row.names = F)
write.csv(sharpe.ls, paste0(wd,"/realdata4select/sharpels.csv"), row.names = F)
write.csv(mumaxw.ls, paste0(wd,"/realdata4select/mumaxwls.csv"), row.names = F)
write.csv(muminw.ls, paste0(wd,"/realdata4select/muminwls.csv"), row.names = F)
write.csv(mulong.ls, paste0(wd,"/realdata4select/mulongls.csv"), row.names = F)
write.csv(mushort.ls, paste0(wd,"/realdata4select/mushortls.csv"), row.names = F)
write.csv(turnover.ls, paste0(wd,"/realdata4select/turnoverls.csv"), row.names = F)
```

## Load data
```{r}
# LASSO
muret.ls = read.csv(paste0(wd,"/realdata4select/muretls.csv"))[[1]]
musd.ls = read.csv(paste0(wd,"/realdata4select/musdls.csv"))[[1]]
sharpe.ls = read.csv(paste0(wd,"/realdata4select/sharpels.csv"))[[1]]
mumaxw.ls = read.csv(paste0(wd,"/realdata4select/mumaxwls.csv"))[[1]]
muminw.ls = read.csv(paste0(wd,"/realdata4select/muminwls.csv"))[[1]]
mulong.ls = read.csv(paste0(wd,"/realdata4select/mulongls.csv"))[[1]]
mushort.ls = read.csv(paste0(wd,"/realdata4select/mushortls.csv"))[[1]]
muexp.ls = read.csv(paste0(wd,"/realdata4select/muexpls.csv"))[[1]]
turnover.ls = read.csv(paste0(wd,"/realdata4select/turnoverls.csv"))[[1]]
```

# Analysis
```{r}
testlam = c(1, 5e-01, 1e-01, 5e-02, 1e-02, 5e-03, 1e-03, 5e-04, 1e-04)
print(testlam)
print(muret.ls)
print(musd.ls)
print(sharpe.ls)
print(mumaxw.ls)
print(muminw.ls)
print(mulong.ls)
print(mushort.ls)
print(turnover.ls)
print(muexp.ls)
```
