---
title: "Simulation for 500 Assets"
author: "Jeremiah"
date: "08 May 2018"
output: pdf_document
---

# This RMD file documents the code for the analysis of the simulated returns data using 500 assets.

```{r setup, include=FALSE}
# Set working directory
wd = "C:/Users/Michael Tay/Desktop/Project"
# Load libraries and functions
source(paste0(wd,"/functionlist.r"))
library(MASS)
library(LiblineaR)
library(rqPen)
library(quadprog)
library(glmnet)
library(beepr)
```

## Define Experiment Parameters

```{r}
n.sim = 500 # Number of simulations
n = 252 # Number of data points i.e. trading days
p1 = 200 # Number of assets for non-degenerate case
p2 = 500 # Number of assets for degenerate case
train.portion = 11/12
test.portion = 1/12
train.size = ceiling(n*train.portion)
test.size = floor(n*test.portion)
```

## Generate Returns Data
### Generate 500 independent sets of returns data for non-degenerate (p=200) and degenerate cases (p=500) with n = 252. We store them and read them later on for convenience. The generate returns and covariance matrix of each simulation is appended to the bottom of the previous simulation in the following order: Returns of simulation 1, Variance of simulation 1, Returns of simlation 2, variance of simulation 2, ...
### For example, returns of simulation 1 will be stored from (1,1) to (n,p), variance of simulation 1 will be stored in (n+1,1) to (n+p, p)

### WARNING: Do not run if data has been previously generated.

```{r}
simdat500 = NULL
for(i in 1:n.sim){  
  sim.i = ff_ret(n, p2)
  ret = sim.i[[1]] # returns data
  varcov = sim.i[[2]] # Var cov
  comb = rbind(ret, varcov)
  simdat500 = rbind(simdat500, comb)
}
write.csv(simdat500, paste0(wd,"/SimData/simdat500.csv", row.names = F))

```

## Load Data
### Read data generated from previous session
```{r}
simdat500 = read.csv(paste0(wd,"/SimData/simdat500.csv"))
```

## Initialise arrays to store interested values

```{r}
# Initialise arrays to store the portfolio expected returns
eret.orc = numeric(n.sim)
eret.gmv = numeric(n.sim)
eret.eq = numeric(n.sim)
eret.svr11 = matrix(numeric(100*n.sim), 100, n.sim)
eret.svr13 = matrix(numeric(100*n.sim), 100, n.sim)
eret.q25 = matrix(numeric(40*n.sim), 40, n.sim)
eret.q50 = matrix(numeric(40*n.sim), 40, n.sim)
eret.q75 = matrix(numeric(40*n.sim), 40, n.sim)
eret.ls = matrix(numeric(100*n.sim), 100, n.sim)

# Initialise arrays to store max and min weights
minw.orc = numeric(n.sim)
maxw.orc = numeric(n.sim)
minw.gmv = numeric(n.sim)
maxw.gmv = numeric(n.sim)
minw.svr11 = matrix(numeric(100*n.sim), 100, n.sim)
maxw.svr11 = matrix(numeric(100*n.sim), 100, n.sim)
minw.svr13 = matrix(numeric(100*n.sim), 100, n.sim)
maxw.svr13 = matrix(numeric(100*n.sim), 100, n.sim)
minw.q25 = matrix(numeric(40*n.sim), 40, n.sim)
maxw.q25 = matrix(numeric(40*n.sim), 40, n.sim)
minw.q50 = matrix(numeric(40*n.sim), 40, n.sim)
maxw.q50 = matrix(numeric(40*n.sim), 40, n.sim)
minw.q75 = matrix(numeric(40*n.sim), 40, n.sim)
maxw.q75 = matrix(numeric(40*n.sim), 40, n.sim)
minw.ls = matrix(numeric(100*n.sim), 100, n.sim)
maxw.ls = matrix(numeric(100*n.sim), 100, n.sim)

# Initialise arrays to store number of long and short positions
long.orc = numeric(n.sim)
short.orc = numeric(n.sim)
long.gmv = numeric(n.sim)
short.gmv = numeric(n.sim)
long.svr11 = matrix(numeric(100*n.sim), 100, n.sim)
short.svr11 = matrix(numeric(100*n.sim), 100, n.sim)
long.svr13 = matrix(numeric(100*n.sim), 100, n.sim)
short.svr13 = matrix(numeric(100*n.sim), 100, n.sim)
long.q25 = matrix(numeric(40*n.sim), 40, n.sim)
short.q25 = matrix(numeric(40*n.sim), 40, n.sim)
long.q50 = matrix(numeric(40*n.sim), 40, n.sim)
short.q50 = matrix(numeric(40*n.sim), 40, n.sim)
long.q75 = matrix(numeric(40*n.sim), 40, n.sim)
short.q75 = matrix(numeric(40*n.sim), 40, n.sim)
long.ls = matrix(numeric(100*n.sim), 100, n.sim)
short.ls = matrix(numeric(100*n.sim), 100, n.sim)

# Initialise matrix to store gross exposure contraint
exp.svr11 = matrix(numeric(100*n.sim), 100, n.sim)
exp.svr13 = matrix(numeric(100*n.sim), 100, n.sim)
exp.q25 = matrix(numeric(40*n.sim), 40, n.sim)
exp.q50 = matrix(numeric(40*n.sim), 40, n.sim)
exp.q75 = matrix(numeric(40*n.sim), 40, n.sim)
exp.ls = matrix(numeric(100*n.sim), 100, n.sim)
```

## Construct Portfolios (Oracle, GMV, Equally Weighted, SVR11, SVR13)
### First analyse data for p = 500

```{r}
for(i in 1:n.sim){
  sim.i = simdat500[((i-1)*(n+p2)+1):(i*(n+p2)), ]
  ret = sim.i[1:n, ] # returns data
  varcov = as.matrix(sim.i[(n+1):(n+p2), ]) # Var cov

  # Split into training and testing dataset
  train = ret[1:train.size,]
  test = ret[(train.size+1):nrow(ret),]
  eret = matrix(apply(test, 2, mean), p2, 1) # Expected returns of test data
  tret = (apply(as.matrix(test)/100 + 1, 2, prod) - 1)*100
  
  # Learning Phase ####
  
  ## Oracle portfolio weights ####
  w.orc = (solve(varcov)%*%matrix(rep(1,p2),p2,1))/sum(solve(varcov)%*%matrix(rep(1,p2),p2,1))
  eret.orc[i] = tret %*% w.orc
  minw.orc[i] = min(w.orc)
  maxw.orc[i] = max(w.orc)
  long.orc[i] = sum(w.orc > 0)
  short.orc[i] = sum(w.orc < 0)
  
  ## Compute Estimated Covariance Matrices from train sets
  ### Sample Covariance
  sc = var(train)

  ## GMV Portfolio doesn't exist for degenerate p=500 case
  ### Instead we use the Generalised Inverse
  w.gmv = (ginv(sc)%*%matrix(rep(1,p2),p2,1))/sum(ginv(sc)%*%matrix(rep(1,p2),p2,1))
  eret.gmv[i] = tret %*% w.gmv
  minw.gmv[i] = min(w.gmv)
  maxw.gmv[i] = max(w.gmv)
  long.gmv[i] = sum(w.gmv > 0)
  short.gmv[i] = sum(w.gmv < 0)


  ## Equally Weighted Porfolio
  w.eq = matrix(rep(1/p2, p2), p2, 1)
  eret.eq[i] = tret %*% w.eq

  
  ## Using SVR ####
  #### Put training returns data into appropriate regression form
  mydat = trans.phi(train)
  y = mydat$Y
  x = as.matrix(mydat[,2:ncol(mydat)])
  
  ### Support Vector Regression LiblineaR - L2-reg, L2-loss (Primal) --> svr11
  ### Test SVR-11 model
  testc = seq(0.00003, 0.3, length = 100)
  for(j in 1:length(testc)){
    svr11 = LiblineaR(x, y, type = 11, cost = testc[j], epsilon = 0.01, bias = TRUE, svr_eps = sd(y))
    w.svr11_pm1 = svr11$W[-length(svr11$W)]  # Remove intercept coefficient
    # All weights of magnitude under the threshold 0.001 are considered negligible and excluded
    w.svr11_pm1[abs(w.svr11_pm1) < 0.001] = 0
    # The optimal weights does not include the weight of asset p
    w.svr11_p = 1 - sum(w.svr11_pm1)
    w.svr11 = matrix(c(w.svr11_pm1, w.svr11_p), p2, 1)
    
    # Gross Exposure
    exp.svr11[j, i] = sum(abs(w.svr11))
    # Porfolio return
    eret.svr11[j, i] =  tret %*% w.svr11
    # Store min and max weights
    minw.svr11[j, i] = min(w.svr11)
    maxw.svr11[j, i] = max(w.svr11)
    # Store  number of short and long positions
    long.svr11[j, i] = sum(w.svr11 > 0)
    short.svr11[j, i] = sum(w.svr11 < 0)
  }

  ### Support Vector Regression LiblineaR - L2-reg, L1-loss (Dual) --> svr13
  ### Test SVR-13 model
  for(j in 1:length(testc)){
    svr13 = LiblineaR(x, y, type = 13, cost = testc[j], epsilon = 0.01, bias = TRUE, svr_eps = sd(y))
    w.svr13_pm1 = svr13$W[-length(svr13$W)]  # Remove intercept coefficient
    # All weights of magnitude under the threshold 0.001 are considered negligible and excluded
    w.svr13_pm1[abs(w.svr13_pm1) < 0.001] = 0
    # The optimal weights does not include the weight of asset p
    w.svr13_p = 1 - sum(w.svr13_pm1)
    w.svr13 = matrix(c(w.svr13_pm1, w.svr13_p), p2, 1)
    
    # Gross Exposure
    exp.svr13[j, i] = sum(abs(w.svr13))
    # Porfolio return
    eret.svr13[j, i] =  tret %*% w.svr13
    # All weights of magnitude under the threshold 0.001 are considered negligible and excluded
    w.svr13[abs(w.svr13) < 0.001] = 0
    # Store min and max weights
    minw.svr13[j, i] = min(w.svr13)
    maxw.svr13[j, i] = max(w.svr13)
    # Store  number of short and long positions
    long.svr13[j, i] = sum(w.svr13 > 0)
    short.svr13[j, i] = sum(w.svr13 < 0)
  }
    if(i %in% seq(50, 450, 50)){
    print(paste("Progress...", paste0(i/50,"/10")))
  }
}
beep(8)
print("Complete!")
```

## Compute Key features of Results from Simulation Studies
### First save the results of the mean returns, SD, Sharpe ratio, Max weight, Min weight and the number of long and short positions from the 500 simulations

```{r}
muret.orc = mean(eret.orc)
musd.orc = sd(eret.orc)
sharpe.orc = muret.orc/musd.orc
mumaxw.orc = mean(maxw.orc)
muminw.orc = mean(minw.orc)
mulong.orc = round(mean(long.orc))
mushort.orc = round(mean(short.orc))
write.csv(muret.orc, paste0(wd,"/p500 Results 4/muretorc.csv"), row.names = F)
write.csv(musd.orc, paste0(wd,"/p500 Results 4/musdorc.csv"), row.names = F)
write.csv(sharpe.orc, paste0(wd,"/p500 Results 4/sharpeorc.csv"), row.names = F)
write.csv(mumaxw.orc, paste0(wd,"/p500 Results 4/mumaxworc.csv"), row.names = F)
write.csv(muminw.orc, paste0(wd,"/p500 Results 4/muminworc.csv"), row.names = F)
write.csv(mulong.orc, paste0(wd,"/p500 Results 4/mulongorc.csv"), row.names = F)
write.csv(mushort.orc, paste0(wd,"/p500 Results 4/mushortorc.csv"), row.names = F)

muret.gmv = mean(eret.gmv)
musd.gmv = sd(eret.gmv)
sharpe.gmv = muret.gmv/musd.gmv
mumaxw.gmv = mean(maxw.gmv)
muminw.gmv = mean(minw.gmv)
mulong.gmv = round(mean(long.gmv))
mushort.gmv = round(mean(short.gmv))
write.csv(muret.gmv, paste0(wd,"/p500 Results 4/muretgmv.csv"), row.names = F)
write.csv(musd.gmv, paste0(wd,"/p500 Results 4/musdgmv.csv"), row.names = F)
write.csv(sharpe.gmv, paste0(wd,"/p500 Results 4/sharpegmv.csv"), row.names = F)
write.csv(mumaxw.gmv, paste0(wd,"/p500 Results 4/mumaxwgmv.csv"), row.names = F)
write.csv(muminw.gmv, paste0(wd,"/p500 Results 4/muminwgmv.csv"), row.names = F)
write.csv(mulong.gmv, paste0(wd,"/p500 Results 4/mulonggmv.csv"), row.names = F)
write.csv(mushort.gmv, paste0(wd,"/p500 Results 4/mushortgmv.csv"), row.names = F)

muret.eq = mean(eret.eq)
musd.eq = sd(eret.eq)
sharpe.eq = muret.eq/musd.eq
write.csv(muret.eq, paste0(wd,"/p500 Results 4/mureteq.csv"), row.names = F)
write.csv(musd.eq, paste0(wd,"/p500 Results 4/musdeq.csv"), row.names = F)
write.csv(sharpe.eq, paste0(wd,"/p500 Results 4/sharpeeq.csv"), row.names = F)

muret.svr11 = apply(eret.svr11, 1, mean)
musd.svr11 = apply(eret.svr11, 1, sd)
sharpe.svr11 = muret.svr11/musd.svr11
mumaxw.svr11 = apply(maxw.svr11, 1, mean)
muminw.svr11 = apply(minw.svr11, 1, mean)
mulong.svr11 = round(apply(long.svr11, 1, mean))
mushort.svr11 = round(apply(short.svr11, 1, mean))
muexp.svr11 = apply(exp.svr11, 1, mean)
write.csv(muexp.svr11, paste0(wd,"/p500 Results 4/muexpsvr11.csv"), row.names = F)
write.csv(muret.svr11, paste0(wd,"/p500 Results 4/muretsvr11.csv"), row.names = F)
write.csv(musd.svr11, paste0(wd,"/p500 Results 4/musdsvr11.csv"), row.names = F)
write.csv(sharpe.svr11, paste0(wd,"/p500 Results 4/sharpesvr11.csv"), row.names = F)
write.csv(mumaxw.svr11, paste0(wd,"/p500 Results 4/mumaxwsvr11.csv"), row.names = F)
write.csv(muminw.svr11, paste0(wd,"/p500 Results 4/muminwsvr11.csv"), row.names = F)
write.csv(mulong.svr11, paste0(wd,"/p500 Results 4/mulongsvr11.csv"), row.names = F)
write.csv(mushort.svr11, paste0(wd,"/p500 Results 4/mushortsvr11.csv"), row.names = F)

muret.svr13 = apply(eret.svr13, 1, mean)
musd.svr13 = apply(eret.svr13, 1, sd)
sharpe.svr13 = muret.svr13/musd.svr13
mumaxw.svr13 = apply(maxw.svr13, 1, mean)
muminw.svr13 = apply(minw.svr13, 1, mean)
mulong.svr13 = round(apply(long.svr13, 1, mean))
mushort.svr13 = round(apply(short.svr13, 1, mean))
muexp.svr13 = apply(exp.svr13, 1, mean)
write.csv(muexp.svr13, paste0(wd,"/p500 Results 4/muexpsvr13.csv"), row.names = F)
write.csv(muret.svr13, paste0(wd,"/p500 Results 4/muretsvr13.csv"), row.names = F)
write.csv(musd.svr13, paste0(wd,"/p500 Results 4/musdsvr13.csv"), row.names = F)
write.csv(sharpe.svr13, paste0(wd,"/p500 Results 4/sharpesvr13.csv"), row.names = F)
write.csv(mumaxw.svr13, paste0(wd,"/p500 Results 4/mumaxwsvr13.csv"), row.names = F)
write.csv(muminw.svr13, paste0(wd,"/p500 Results 4/muminwsvr13.csv"), row.names = F)
write.csv(mulong.svr13, paste0(wd,"/p500 Results 4/mulongsvr13.csv"), row.names = F)
write.csv(mushort.svr13, paste0(wd,"/p500 Results 4/mushortsvr13.csv"), row.names = F)
```
## Load data from previous session
```{r}
muret.eq = read.csv(paste0(wd,"/p500 Results 4/mureteq.csv"))[[1]]
musd.eq = read.csv(paste0(wd,"/p500 Results 4/musdeq.csv"))[[1]]
sharpe.eq = read.csv(paste0(wd,"/p500 Results 4/sharpeeq.csv"))[[1]]

muret.orc = read.csv(paste0(wd,"/p500 Results 4/muretorc.csv"))[[1]]
musd.orc = read.csv(paste0(wd,"/p500 Results 4/musdorc.csv"))[[1]]
sharpe.orc = read.csv(paste0(wd,"/p500 Results 4/sharpeorc.csv"))[[1]]
mumaxw.orc = read.csv(paste0(wd,"/p500 Results 4/mumaxworc.csv"))[[1]]
muminw.orc = read.csv(paste0(wd,"/p500 Results 4/muminworc.csv"))[[1]]
mulong.orc = read.csv(paste0(wd,"/p500 Results 4/mulongorc.csv"))[[1]]
mushort.orc = read.csv(paste0(wd,"/p500 Results 4/mushortorc.csv"))[[1]]

muret.gmv = read.csv(paste0(wd,"/p500 Results 4/muretgmv.csv"))[[1]]
musd.gmv = read.csv(paste0(wd,"/p500 Results 4/musdgmv.csv"))[[1]]
sharpe.gmv = read.csv(paste0(wd,"/p500 Results 4/sharpegmv.csv"))[[1]]
mumaxw.gmv = read.csv(paste0(wd,"/p500 Results 4/mumaxwgmv.csv"))[[1]]
muminw.gmv = read.csv(paste0(wd,"/p500 Results 4/muminwgmv.csv"))[[1]]
mulong.gmv = read.csv(paste0(wd,"/p500 Results 4/mulonggmv.csv"))[[1]]
mushort.gmv = read.csv(paste0(wd,"/p500 Results 4/mushortgmv.csv"))[[1]]

muret.svr11 = read.csv(paste0(wd,"/p500 Results 4/muretsvr11.csv"))[[1]]
musd.svr11 = read.csv(paste0(wd,"/p500 Results 4/musdsvr11.csv"))[[1]]
sharpe.svr11 = read.csv(paste0(wd,"/p500 Results 4/sharpesvr11.csv"))[[1]]
mumaxw.svr11 = read.csv(paste0(wd,"/p500 Results 4/mumaxwsvr11.csv"))[[1]]
muminw.svr11 = read.csv(paste0(wd,"/p500 Results 4/muminwsvr11.csv"))[[1]]
mulong.svr11 = read.csv(paste0(wd,"/p500 Results 4/mulongsvr11.csv"))[[1]]
mushort.svr11 = read.csv(paste0(wd,"/p500 Results 4/mushortsvr11.csv"))[[1]]
muexp.svr11 =  read.csv(paste0(wd,"/p500 Results 4/muexpsvr11.csv"))[[1]]

muret.svr13 = read.csv(paste0(wd,"/p500 Results 4/muretsvr13.csv"))[[1]]
musd.svr13 = read.csv(paste0(wd,"/p500 Results 4/musdsvr13.csv"))[[1]]
sharpe.svr13 = read.csv(paste0(wd,"/p500 Results 4/sharpesvr13.csv"))[[1]]
mumaxw.svr13 = read.csv(paste0(wd,"/p500 Results 4/mumaxwsvr13.csv"))[[1]]
muminw.svr13 = read.csv(paste0(wd,"/p500 Results 4/muminwsvr13.csv"))[[1]]
mulong.svr13 = read.csv(paste0(wd,"/p500 Results 4/mulongsvr13.csv"))[[1]]
mushort.svr13 = read.csv(paste0(wd,"/p500 Results 4/mushortsvr13.csv"))[[1]]
muexp.svr13 =  read.csv(paste0(wd,"/p500 Results 4/muexpsvr13.csv"))[[1]]
```


### Relationship between the regularisation parameter c, gross exposure constraint and number of stocks selected
```{r}
##### SVR11
testc = seq(0.00003, 0.3, length = 100)
plot(testc, muexp.svr11, type = "l", xlab = "Regularisation Parameter", ylab = "Gross Exposure", main = "L2 Reg L2 Loss SVR")
plot(testc, mulong.svr11+mushort.svr11, type = "l", xlab = "Regularisation Parameter", ylab = "Number of Stocks", main = "L2 Reg L2 Loss SVR")
#### SVR13
plot(testc, muexp.svr13, type = "l", xlab = "Regularisation Parameter", ylab = "Gross Exposure", main = "L2 Reg L1 Loss SVR")
plot(testc, mulong.svr13+mushort.svr13, type = "l", xlab = "Regularisation Parameter", ylab = "Number of Stocks", main = "L2 Reg L1 Loss SVR")
```

## Analysis of Results from Simulation Studies
### We are interest in the features of 5 selected values of c i.e. c = 0.0005, 0.005, 0.01, 0.05, 0.1
### We look at the mean returns, SD, Sharpe ratio, Max weight, Min weight and the number of long and short positions from the 500 simulations of the Oracle portfolio
```{r}
print(muret.orc)
print(musd.orc)
print(sharpe.orc)
print(mumaxw.orc)
print(muminw.orc)
print(mulong.orc)
print(mushort.orc)
```

## Analysis of Results from Simulation Studies with SVR 11
### We look at the mean returns, SD, Sharpe ratio, Max weight, Min weight and the number of long and short positions from the 500 simulations
### The gross exposures will not be exactly 1, 1.5, 2 ,etc. but they will be very close.
```{r}
paste(muexp.svr11[1], muexp.svr11[100])
c1 = which(abs(muexp.svr11 - 1) == min(abs(muexp.svr11 - 1)))
c1.5 = which(abs(muexp.svr11 - 1.5) == min(abs(muexp.svr11 - 1.5)))
c2 = which(abs(muexp.svr11 - 2) == min(abs(muexp.svr11 - 2)))
ind = c(c1, c1.5, c2)
testc[ind]
muret.svr11x = muret.svr11[ind]
musd.svr11x = musd.svr11[ind]
sharpe.svr11x = sharpe.svr11[ind]
mumaxw.svr11x = mumaxw.svr11[ind]
muminw.svr11x = muminw.svr11[ind]
mulong.svr11x = mulong.svr11[ind]
mushort.svr11x = mushort.svr11[ind]
print(muret.svr11x)
print(musd.svr11x)
print(sharpe.svr11x)
print(mumaxw.svr11x)
print(muminw.svr11x)
print(mulong.svr11x)
print(mushort.svr11x)
```

## Analysis of Results from Simulation Studies with SVR 13
### We look at the mean returns, SD, Sharpe ratio, Max weight, Min weight and the number of long and short positions from the 500 simulations
```{r}
paste(muexp.svr13[1], muexp.svr13[100])
c1 = which(abs(muexp.svr11 - 1) == min(abs(muexp.svr11 - 1)))
c1.5 = which(abs(muexp.svr11 - 1.5) == min(abs(muexp.svr11 - 1.5)))
c2 = which(abs(muexp.svr11 - 2) == min(abs(muexp.svr11 - 2)))
ind2 = c(c1, c1.5, c2)
testc[ind2]
muret.svr13x = muret.svr13[ind2]
musd.svr13x = musd.svr13[ind2]
sharpe.svr13x = sharpe.svr13[ind2]
mumaxw.svr13x = mumaxw.svr13[ind2]
muminw.svr13x = muminw.svr13[ind2]
mulong.svr13x = mulong.svr13[ind2]
mushort.svr13x = mushort.svr13[ind2]
print(muret.svr13x)
print(musd.svr13x)
print(sharpe.svr13x)
print(mumaxw.svr13x)
print(muminw.svr13x)
print(mulong.svr13x)
print(mushort.svr13x)
```


## Analysis of Results from Simulation Studies with GMV
### We look at the mean returns, SD, Sharpe ratio, Max weight, Min weight and the number of long and short positions from the 500 simulations
```{r}
print(muret.gmv)
print(musd.gmv)
print(sharpe.gmv)
print(mumaxw.gmv)
print(muminw.gmv)
print(mulong.gmv)
print(mushort.gmv)
```

## Analysis of Results from Simulation Studies with Equally Weighted Portfolio
### We look at the mean returns, SD, Sharpe ratio, Max weight, Min weight and the number of long and short positions from the 500 simulations
```{r}
print(muret.eq)
print(musd.eq)
print(sharpe.eq)
```

## Construct Portfolios (L1 Regularized Quantile Regression) for p = 500

```{r}
for(i in 1:n.sim){
  sim.i = simdat500[((i-1)*(n+p2)+1):(i*(n+p2)), ]
  ret = sim.i[1:n, ] # returns data
  varcov = as.matrix(sim.i[(n+1):(n+p2), ]) # Var cov
  
  # Split into training and testing dataset
  train = ret[1:train.size,]
  test = ret[(train.size+1):nrow(ret),]
  eret = matrix(apply(test, 2, mean), p2, 1) # Expected returns of test data
  tret = (apply(as.matrix(test)/100 + 1, 2, prod) - 1)*100
    
  # Learning Phase ####

  ## Using Quantile Regression ####
  #### Put training returns data into appropriate regression form
  mydat = trans.phi(train)
  y = mydat$Y
  x = as.matrix(mydat[,2:ncol(mydat)])
  
  ### Lasso Penalized Quantile Regression using rqPen
  ### Test Quantile model - 50% Quantile
  #### Dithering the response variable is frequently a useful option in quantile regression fitting to avoid deleterious effects of degenerate solutions     (Machado and Santos Silva, 2005)
  testlam = seq(0.01, 0.2, length = 40)
  for(j in 1:length(testlam)){
    y50 = y # Dither y50 instead of the actual vector y
    q50 = NULL
    while(is.null(q50)){
      try({q50 = LASSO.fit(y50, x, tau = .5, lambda = testlam[j], intercept = TRUE, coef.cutoff = 1e-03)}, silent = T)
      if(is.null(q50)) y50 = dither(y, type = "symmetric", value = 0.0001)
    }
    # The optimal weights does not include the weight of asset p
    w.q50_p = 1 - sum(q50[2:length(q50)]) # First coef is the intercept
    w.q50 = matrix(c(q50[2:length(q50)], w.q50_p), p2, 1)
    # Store gross exposure
    exp.q50[j, i] = sum(abs(w.q50))
    # Porfolio return
    eret.q50[j, i] =  tret %*% w.q50
    # Store min and max weights
    minw.q50[j, i] = min(w.q50)
    maxw.q50[j, i] = max(w.q50)
    # Store  number of short and long positions
    long.q50[j, i] = sum(w.q50 > 0)
    short.q50[j, i] = sum(w.q50 < 0)
  }
  
  ### Test Quantile model - 25% Quantile
  for(j in 1:length(testlam)){
    y25 = y # Dither y25 instead of the actual vector y
    q25 = NULL
    while(is.null(q25)){
      try({q25 = LASSO.fit(y25, x, tau = .25, lambda = testlam[j], intercept = TRUE, coef.cutoff = 1e-03)}, silent = T)
      if(is.null(q25)) y25 = dither(y25, type = "symmetric", value = 0.0001)
    }
    # The optimal weights does not include the weight of asset p
    w.q25_p = 1 - sum(q25[2:length(q25)])
    w.q25 = matrix(c(q25[2:length(q25)], w.q25_p), p2, 1)
    # Store gross exposure
    exp.q25[j, i] = sum(abs(w.q25))
    # Porfolio return
    eret.q25[j, i] =   tret %*% w.q25
    # Store min and max weights
    minw.q25[j, i] = min(w.q25)
    maxw.q25[j, i] = max(w.q25)
    # Store  number of short and long positions
    long.q25[j, i] = sum(w.q25 > 0)
    short.q25[j, i] = sum(w.q25 < 0)
  }
    
  ### Test Quantile model - 75% Quantile
  for(j in 1:length(testlam)){
    y75 = y # Dither y75 instead of the actual vector y
    q75 = NULL
    while(is.null(q75)){
      try({q75 = LASSO.fit(y75, x, tau = .75, lambda = testlam[j], intercept = TRUE, coef.cutoff = 1e-03)}, silent = T)
      if(is.null(q75)) y75 = dither(y75, type = "symmetric", value = 0.0001)
    }
    # The optimal weights does not include the weight of asset p
    w.q75_p = 1 - sum(q75[2:length(q75)])
    w.q75 = matrix(c(q75[2:length(q75)], w.q75_p), p2, 1)
    # Store gross exposure
    exp.q75[j, i] = sum(abs(w.q75))
    # Porfolio return
    eret.q75[j, i] =   tret %*% w.q75
    # Store min and max weights
    minw.q75[j, i] = min(w.q75)
    maxw.q75[j, i] = max(w.q75)
    # Store  number of short and long positions
    long.q75[j, i] = sum(w.q75 > 0)
    short.q75[j, i] = sum(w.q75 < 0)
   }
  if(i %in% seq(50, 450, 50)){
    print(paste("Progress...", paste0(i/50,"/10")))
  }
}
beep(8)
print("Complete!")
```


## Save Results
```{r}
muret.q50 = apply(eret.q50x, 1, mean)
musd.q50 = apply(eret.q50x, 1, sd)
sharpe.q50 = muret.q50/musd.q50
mumaxw.q50 = apply(maxw.q50x, 1, mean)
muminw.q50 = apply(minw.q50x, 1, mean)
mulong.q50 = round(apply(long.q50x, 1, mean))
mushort.q50 = round(apply(short.q50x, 1, mean))
muexp.q50 = apply(exp.q50x, 1, mean)
write.csv(muexp.q50, paste0(wd,"/p500 Results 4/muexpq502.csv"), row.names = F)
write.csv(muret.q50, paste0(wd,"/p500 Results 4/muretq502.csv"), row.names = F)
write.csv(musd.q50, paste0(wd,"/p500 Results 4/musdq502.csv"), row.names = F)
write.csv(sharpe.q50, paste0(wd,"/p500 Results 4/sharpeq502.csv"), row.names = F)
write.csv(mumaxw.q50, paste0(wd,"/p500 Results 4/mumaxwq502.csv"), row.names = F)
write.csv(muminw.q50, paste0(wd,"/p500 Results 4/muminwq502.csv"), row.names = F)
write.csv(mulong.q50, paste0(wd,"/p500 Results 4/mulongq502.csv"), row.names = F)
write.csv(mushort.q50, paste0(wd,"/p500 Results 4/mushortq502.csv"), row.names = F)

muret.q25 = apply(eret.q25x, 1, mean)
musd.q25 = apply(eret.q25x, 1, sd)
sharpe.q25 = muret.q25/musd.q25
mumaxw.q25 = apply(maxw.q25x, 1, mean)
muminw.q25 = apply(minw.q25x, 1, mean)
mulong.q25 = round(apply(long.q25x, 1, mean))
mushort.q25 = round(apply(short.q25x, 1, mean))
muexp.q25 = apply(exp.q25x, 1, mean)
write.csv(muexp.q25, paste0(wd, "/p500 Results 4/muexpq252.csv"), row.names = F)
write.csv(muret.q25, paste0(wd,"/p500 Results 4/muretq252.csv"), row.names = F)
write.csv(musd.q25, paste0(wd,"/p500 Results 4/musdq252.csv"), row.names = F)
write.csv(sharpe.q25, paste0(wd,"/p500 Results 4/sharpeq252.csv"), row.names = F)
write.csv(mumaxw.q25, paste0(wd,"/p500 Results 4/mumaxwq252.csv"), row.names = F)
write.csv(muminw.q25, paste0(wd,"/p500 Results 4/muminwq252.csv"), row.names = F)
write.csv(mulong.q25, paste0(wd,"/p500 Results 4/mulongq252.csv"), row.names = F)
write.csv(mushort.q25, paste0(wd,"/p500 Results 4/mushortq252.csv"), row.names = F)

muret.q75 = apply(eret.q75, 1, mean)
musd.q75 = apply(eret.q75, 1, sd)
sharpe.q75 = muret.q75/musd.q75
mumaxw.q75 = apply(maxw.q75, 1, mean)
muminw.q75 = apply(minw.q75, 1, mean)
mulong.q75 = round(apply(long.q75, 1, mean))
mushort.q75 = round(apply(short.q75, 1, mean))
muexp.q75 = apply(exp.q75, 1, mean)
write.csv(muexp.q75, paste0(wd, "/p500 Results 4/muexpq752.csv"), row.names = F)
write.csv(muret.q75, paste0(wd,"/p500 Results 4/muretq752.csv"), row.names = F)
write.csv(musd.q75, paste0(wd,"/p500 Results 4/musdq752.csv"), row.names = F)
write.csv(sharpe.q75, paste0(wd,"/p500 Results 4/sharpeq752.csv"), row.names = F)
write.csv(mumaxw.q75, paste0(wd,"/p500 Results 4/mumaxwq752.csv"), row.names = F)
write.csv(muminw.q75, paste0(wd,"/p500 Results 4/muminwq752.csv"), row.names = F)
write.csv(mulong.q75, paste0(wd,"/p500 Results 4/mulongq752.csv"), row.names = F)
write.csv(mushort.q75, paste0(wd,"/p500 Results 4/mushortq752.csv"), row.names = F)
```

## Load data
```{r}
# q50
muret.q50 = read.csv(paste0(wd,"/p500 Results 4/muretq50.csv"))[[1]]
musd.q50 = read.csv(paste0(wd,"/p500 Results 4/musdq50.csv"))[[1]]
sharpe.q50 = read.csv(paste0(wd,"/p500 Results 4/sharpeq50.csv"))[[1]]
mumaxw.q50 = read.csv(paste0(wd,"/p500 Results 4/mumaxwq50.csv"))[[1]]
muminw.q50 = read.csv(paste0(wd,"/p500 Results 4/muminwq50.csv"))[[1]]
mulong.q50 = read.csv(paste0(wd,"/p500 Results 4/mulongq50.csv"))[[1]]
mushort.q50 = read.csv(paste0(wd,"/p500 Results 4/mushortq50.csv"))[[1]]
muexp.q50 = read.csv(paste0(wd,"/p500 Results 4/muexpq50.csv"))[[1]]

# q25
muret.q25 = read.csv(paste0(wd,"/p500 Results 4/muretq25.csv"))[[1]]
musd.q25 = read.csv(paste0(wd,"/p500 Results 4/musdq25.csv"))[[1]]
sharpe.q25 = read.csv(paste0(wd,"/p500 Results 4/sharpeq25.csv"))[[1]]
mumaxw.q25 = read.csv(paste0(wd,"/p500 Results 4/mumaxwq25.csv"))[[1]]
muminw.q25 = read.csv(paste0(wd,"/p500 Results 4/muminwq25.csv"))[[1]]
mulong.q25 = read.csv(paste0(wd,"/p500 Results 4/mulongq25.csv"))[[1]]
mushort.q25 = read.csv(paste0(wd,"/p500 Results 4/mushortq25.csv"))[[1]]
muexp.q25 = read.csv(paste0(wd,"/p500 Results 4/muexpq25.csv"))[[1]]

# q75
muret.q75 = read.csv(paste0(wd,"/p500 Results 4/muretq75.csv"))[[1]]
musd.q75 = read.csv(paste0(wd,"/p500 Results 4/musdq75.csv"))[[1]]
sharpe.q75 = read.csv(paste0(wd,"/p500 Results 4/sharpeq75.csv"))[[1]]
mumaxw.q75 = read.csv(paste0(wd,"/p500 Results 4/mumaxwq75.csv"))[[1]]
muminw.q75 = read.csv(paste0(wd,"/p500 Results 4/muminwq75.csv"))[[1]]
mulong.q75 = read.csv(paste0(wd,"/p500 Results 4/mulongq75.csv"))[[1]]
mushort.q75 = read.csv(paste0(wd,"/p500 Results 4/mushortq75.csv"))[[1]]
muexp.q75 = read.csv(paste0(wd,"/p500 Results 4/muexpq75.csv"))[[1]]
```

### Relationship between the regularisation parameter c, gross exposure constraint and number of stocks selected
```{r}
#### q50
testlam = seq(0.01, 0.2, length = 40)
plot(testlam, muexp.q50, type = "l", xlab = "Regularisation Parameter", ylab = "Gross Exposure", main = "L1 Reg Quantile Regression, tau = 0.5")
plot(testlam, mulong.q50+mushort.q50, type = "l", xlab = "Regularisation Parameter", ylab = "Number of stocks", main = "L1 Reg Quantile Regression, tau = 0.5")
##### q25
plot(testlam, muexp.q25, type = "l", xlab = "Regularisation Parameter", ylab = "Gross Exposure", main = "L1 Reg Quantile Regression, tau = 0.25")
plot(testlam, mulong.q25+mushort.q25, type = "l", xlab = "Regularisation Parameter", ylab = "Number of stocks", main = "L1 Reg Quantile Regression, tau = 0.25")
##### q25
plot(testlam, muexp.q75, type = "l", xlab = "Regularisation Parameter", ylab = "Gross Exposure", main = "L1 Reg Quantile Regression, tau = 0.75")
plot(testlam, mulong.q75+mushort.q75, type = "l", xlab = "Regularisation Parameter", ylab = "Number of stocks", main = "L1 Reg Quantile Regression, tau = 0.75")
```

## Analysis of Results from Simulation Studies with quantile regression, Q50
### We look at the mean returns, SD, Sharpe ratio, Max weight, Min weight and the number of long and short positions from the 500 simulations
```{r}
# q50
testlam = seq(0.01, 0.2, length = 40)
paste(muexp.q50[1], muexp.q50[40])
c1 = which(abs(muexp.q50 - 1) == min(abs(muexp.q50 - 1)))
c1.5 = which(abs(muexp.q50 - 1.5) == min(abs(muexp.q50 - 1.5)))
c2 = which(abs(muexp.q50 - 2) == min(abs(muexp.q50 - 2)))
c2.5 = which(abs(muexp.q50 - 2.5) == min(abs(muexp.q50 - 2.5)))
c3 = which(abs(muexp.q50 - 3) == min(abs(muexp.q50 - 3)))
c3.5 = which(abs(muexp.q50 - 3.5) == min(abs(muexp.q50 - 3.5)))
ind2 = c(c1, c1.5, c2, c2.5, c3, c3.5)
muexp.q50[ind2]
muret.q50x = muret.q50[ind2]
musd.q50x = musd.q50[ind2]
sharpe.q50x = sharpe.q50[ind2]
mumaxw.q50x = mumaxw.q50[ind2]
muminw.q50x = muminw.q50[ind2]
mulong.q50x = mulong.q50[ind2]
mushort.q50x = mushort.q50[ind2]
print(muret.q50x)
print(musd.q50x)
print(sharpe.q50x)
print(mumaxw.q50x)
print(muminw.q50x)
print(mulong.q50x)
print(mushort.q50x)
```


## Analysis of Results from Simulation Studies with quantile regression, Q25
### We look at the mean returns, SD, Sharpe ratio, Max weight, Min weight and the number of long and short positions from the 500 simulations
```{r}
# q25
testlam = seq(0.01, 0.2, length = 40)
paste(muexp.q25[1], muexp.q25[40])
c1 = which(abs(muexp.q25 - 1) == min(abs(muexp.q25 - 1)))
c1.5 = which(abs(muexp.q25 - 1.5) == min(abs(muexp.q25 - 1.5)))
c2 = which(abs(muexp.q25 - 2) == min(abs(muexp.q25 - 2)))
c2.5 = which(abs(muexp.q25 - 2.5) == min(abs(muexp.q25 - 2.5)))
c3 = which(abs(muexp.q25 - 3) == min(abs(muexp.q25 - 3)))
c3.5 = which(abs(muexp.q25 - 3.5) == min(abs(muexp.q25 - 3.5)))
ind2 = c(c1, c1.5, c2, c2.5, c3, c3.5)
muexp.q25[ind2]
muret.q25x = muret.q25[ind2]
musd.q25x = musd.q25[ind2]
sharpe.q25x = sharpe.q25[ind2]
mumaxw.q25x = mumaxw.q25[ind2]
muminw.q25x = muminw.q25[ind2]
mulong.q25x = mulong.q25[ind2]
mushort.q25x = mushort.q25[ind2]
print(muret.q25x)
print(musd.q25x)
print(sharpe.q25x)
print(mumaxw.q25x)
print(muminw.q25x)
print(mulong.q25x)
print(mushort.q25x)
```

## Analysis of Results from Simulation Studies with quantile regression, Q75
### We look at the mean returns, SD, Sharpe ratio, Max weight, Min weight and the number of long and short positions from the 500 simulations
```{r}
# q75
testlam = seq(0.01, 0.2, length = 40)
paste(muexp.q75[1], muexp.q75[40])
c1 = which(abs(muexp.q75 - 1) == min(abs(muexp.q75 - 1)))
c1.5 = which(abs(muexp.q75 - 1.5) == min(abs(muexp.q75 - 1.5)))
c2 = which(abs(muexp.q75 - 2) == min(abs(muexp.q75 - 2)))
c2.5 = which(abs(muexp.q75 - 2.5) == min(abs(muexp.q75 - 2.5)))
c3 = which(abs(muexp.q75 - 3) == min(abs(muexp.q75 - 3)))
c3.5 = which(abs(muexp.q75 - 3.5) == min(abs(muexp.q75 - 3.5)))
ind2 = c(c1, c1.5, c2, c2.5, c3, c3.5)
muexp.q75[ind2]
muret.q75x = muret.q75[ind2]
musd.q75x = musd.q75[ind2]
sharpe.q75x = sharpe.q75[ind2]
mumaxw.q75x = mumaxw.q75[ind2]
muminw.q75x = muminw.q75[ind2]
mulong.q75x = mulong.q75[ind2]
mushort.q75x = mushort.q75[ind2]
print(muret.q75x)
print(musd.q75x)
print(sharpe.q75x)
print(mumaxw.q75x)
print(muminw.q75x)
print(mulong.q75x)
print(mushort.q75x)
```

## Construct Portfolios (L1 Regularized Regression - LASSO) for p = 500
```{r}
for(i in 1:n.sim){
  sim.i = simdat500[((i-1)*(n+p2)+1):(i*(n+p2)), ]
  ret = sim.i[1:n, ] # returns data
  varcov = as.matrix(sim.i[(n+1):(n+p2), ]) # Var cov
  
  # Split into training and testing dataset
  train = ret[1:train.size,]
  test = ret[(train.size+1):nrow(ret),]
  eret = matrix(apply(test, 2, mean), p2, 1) # Expected returns of test data
  tret = (apply(as.matrix(test)/100 + 1, 2, prod) - 1)*100
  
  # Learning Phase ####

  ## Using LASSO Regression ####
  #### Put training returns data into appropriate regression form
  mydat = trans.phi(train)
  y = mydat$Y
  x = as.matrix(mydat[,2:ncol(mydat)])
  
  ### Lasso Regression
  testlam = 10^seq(-3, 0.1, length = 100)
  ls.net = glmnet(x, y, alpha = 1, lambda = testlam)
  ls = coef(ls.net)
  for(j in 1:length(testlam)){
    w.ls_pm1.temp = ls[ ,j]
    w.ls_pm1 = w.ls_pm1.temp[2:length(w.ls_pm1.temp)] # First asset is the intercept
    w.ls_p = 1 - sum(w.ls_pm1)
    w.ls = matrix(c(w.ls_pm1, w.ls_p), p2, 1)
    # Store gross exposure
    exp.ls[j, i] = sum(abs(w.ls))
    # Porfolio return
    eret.ls[j, i] =   tret %*% w.ls
    # Store min and max weights
    minw.ls[j, i] = min(w.ls)
    maxw.ls[j, i] = max(w.ls)
    # Store  number of short and long positions
    long.ls[j, i] = sum(w.ls > 0)
    short.ls[j, i] = sum(w.ls < 0)
  }
  if(i %in% seq(50, 450, 50)){
      print(paste("Progress...", paste0(i/50,"/10")))
    }
}
beep(8)
print("Complete!")
```

## Save Results
```{r}
muret.ls = apply(eret.ls, 1, mean)
musd.ls = apply(eret.ls, 1, sd)
sharpe.ls = muret.ls/musd.ls
mumaxw.ls = apply(maxw.ls, 1, mean)
muminw.ls = apply(minw.ls, 1, mean)
mulong.ls = round(apply(long.ls, 1, mean))
mushort.ls = round(apply(short.ls, 1, mean))
muexp.ls = apply(exp.ls, 1, mean)
write.csv(muexp.ls, paste0(wd, "/p500 Results 4/muexpls.csv"), row.names = F)
write.csv(muret.ls, paste0(wd, "/p500 Results 4/muretls.csv"), row.names = F)
write.csv(musd.ls, paste0(wd, "/p500 Results 4/musdls.csv"), row.names = F)
write.csv(sharpe.ls, paste0(wd, "/p500 Results 4/sharpels.csv"), row.names = F)
write.csv(mumaxw.ls, paste0(wd, "/p500 Results 4/mumaxwls.csv"), row.names = F)
write.csv(muminw.ls, paste0(wd, "/p500 Results 4/muminwls.csv"), row.names = F)
write.csv(mulong.ls, paste0(wd, "/p500 Results 4/mulongls.csv"), row.names = F)
write.csv(mushort.ls, paste0(wd, "/p500 Results 4/mushortls.csv"), row.names = F)
```

## Load data
```{r}
# LASSO
muret.ls = read.csv(paste0(wd,"/p500 Results 4/muretls.csv"))[[1]]
musd.ls = read.csv(paste0(wd,"/p500 Results 4/musdls.csv"))[[1]]
sharpe.ls = read.csv(paste0(wd,"/p500 Results 4/sharpels.csv"))[[1]]
mumaxw.ls = read.csv(paste0(wd,"/p500 Results 4/mumaxwls.csv"))[[1]]
muminw.ls = read.csv(paste0(wd,"/p500 Results 4/muminwls.csv"))[[1]]
mulong.ls = read.csv(paste0(wd,"/p500 Results 4/mulongls.csv"))[[1]]
mushort.ls = read.csv(paste0(wd,"/p500 Results 4/mushortls.csv"))[[1]]
muexp.ls = read.csv(paste0(wd,"/p500 Results 4/muexpls.csv"))[[1]]
```

### Relationship between the regularisation parameter c, gross exposure constraint and number of stocks selected
```{r}
#### LASSO
testlam = rev(10^seq(-3, 0.1, length = 100))
plot(testlam, muexp.ls, type = "l", xlab = "Regularisation Parameter", ylab = "Gross Exposure", main = "LASSO Regression")
plot(testlam, mulong.ls+mushort.ls, type = "l", xlab = "Regularisation Parameter", ylab = "Number of stocks", main = "LASSO Regression")
```

## Analysis of Results from Simulation Studies with L1 Regularised Regression - LASSO
### We look at the mean returns, SD, Sharpe ratio, Max weight, Min weight and the number of long and short positions from the 500 simulations
```{r}
paste(muexp.ls[1], muexp.ls[83])
c1 = 17 + which(abs(muexp.ls - 1) == min(abs(muexp.ls - 1)))[1]
c1.5 = which(abs(muexp.ls - 1.5) == min(abs(muexp.ls - 1.5)))
c2 = which(abs(muexp.ls - 2) == min(abs(muexp.ls - 2)))
c2.5 = which(abs(muexp.ls - 2.5) == min(abs(muexp.ls - 2.5)))
c3 = which(abs(muexp.ls - 3) == min(abs(muexp.ls - 3)))
ind = c(c1, c1.5, c2, c2.5, c3)
muexp.ls[ind]
muret.lsx = muret.ls[ind]
musd.lsx = musd.ls[ind]
sharpe.lsx = sharpe.ls[ind]
mumaxw.lsx = mumaxw.ls[ind]
muminw.lsx = muminw.ls[ind]
mulong.lsx = mulong.ls[ind]
mushort.lsx = mushort.ls[ind]
print(muret.lsx)
print(musd.lsx)
print(sharpe.lsx)
print(mumaxw.lsx)
print(muminw.lsx)
print(mulong.lsx)
print(mushort.lsx)
```